### 2021-07-24 paper.tex
methodology done

% font
\usepackage{tgschola}

% sub figure
\usepackage{caption}
\usepackage{subcaption}

\usepackage{graphicx}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{multicol}
\usepackage[ddmmyyyy]{datetime}
\usepackage[a4paper, margin=2cm]{geometry}

@@

	\textbf{ Image Acquisition: } The MRI brain images are acquired and are given as input
	to pre-processing stage. The sample brain MR images are shown in figure 2.

	%\textbf{ Preprocessing: } Preprocessing is needed as it provides improvement  in  image
	%data  which    enhances  some  of  the  image  features  which  are
	%important  for  further  processing.  The    pre-processing  steps  that
	%are  applied  to  MR  image  are as follows :

>>>>

% font
\usepackage{tgschola}
\usepackage{amsmath}

\usepackage{graphicx}
\usepackage{subfig}
\usepackage{float}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{multicol}
\usepackage[ddmmyyyy]{datetime}
\usepackage[a4paper, margin=2cm]{geometry}

@@

	\subsection{Image Acquisition}%
	\label{sub:Image Acquisition}

	The MRI brain images are acquired and are
	given as input to pre-processing stage. The sample brain MR images are shown
	in Figure~\ref{MRIScans}.

	\begin{figure}[H]
		\centering
		\subfloat[MRI scan shown no presence of tumor]
		{\includegraphics[width=0.4\linewidth]
		{imgs/pred1.jpg}\label{scan2}}
		\hspace{0.5cm}
		\subfloat[MRI scan of a tumorous cell]
		{\includegraphics[width=0.3\linewidth]
		{imgs/Y100.JPG}\label{scan1}}
		\caption{MRI Scans}
		\label{MRIScans}
	\end{figure}

	\subsection{Preprocessing}%
	\label{sub:Preprocessing}

	Preprocessing is needed as it provides improvement
	in image data which  enhances some of the image features which are important
	for further processing. The  pre-processing steps that are applied to MR
	image are as follows:

	\begin{enumerate}
		\item The  RGB  MR    image  is  converted  to  gray  scale image  and
			then  median  filter  is  applied  for  noise  removal from brain MR
			images as shown in Figure~\ref{smooted image}. The noise is to removed for further
			processing as high accuracy is needed.

		\item Then  edges  are  detected  from  filtered  image  using canny
			edge  detection  as  shown  in  Figure~\ref{edge detection}.  The  edge detected
			image is needed for segmentation of  the image

		\item Then  watershed  segmentation  is  done  for  finding the
			location  of  the  tumor  in  the  brain  image  as  shown  in
			Figure~\ref{segmentation}. Segmentation is  the process of dividing  an image into
			multiple segments. The aim of segmentation is to change
			representation  of    image  into  something  which  is more  easy
			to  analyze.  The result  of  watershed  segmentation is  label
			image.    In  label  image,  all  the  different  objects identified
			will  have  different  pixel  values  ,  all  the  pixels  of first
			object  will have value 1, all the pixels of second object will have
			value 2 and so on.
	\end{enumerate}

	\begin{figure}[H]
		\centering
		\subfloat[Original Image]
		{\includegraphics[width=0.2\linewidth]
		{imgs/Y100.JPG}\label{original}}
		\hspace{0.5cm}
		\subfloat[Filtered Imaage]
		{\includegraphics[width=0.2\linewidth]
		{imgs/median_filtering.png}\label{smooted image}}
		\hspace{0.5cm}
		\subfloat[Edge Detection]
		{\includegraphics[width=0.2\linewidth]
		{imgs/edges_detection.png}\label{edge detection}}
		\hspace{0.5cm}
		\subfloat[Segmentation]
		{\includegraphics[width=0.2\linewidth]
		{imgs/segmentation.png}\label{segmentation}}
		\caption{preprocessing operations}
		\label{Preprocessing Operations}
	\end{figure}

	\subsection{Feature Extraction}%
	\label{sub:Feature Extraction}

	When input to an algorithm is very large and
	redundant to be processed, it is transformed into reduced representative set
	of features called feature vector. Transformation of input data into set of
	features is called feature extraction. In this step, the important features
	needed for image classification are extracted. The segmented brain MR image
	is used and texture features are extracted from the segmented image which
	shows the texture property of the image. These features are extracted using
	Gray Level Co-occurrence Matrix (GLCM) as it is robust method with high
	performance.

	The GLCM features are extracted as follows:

	\begin{enumerate}
		\item Energy: It gives a measure of textural uniformity, that is, measure
			of pixel pair repetitions.

			\begin{equation}
				E = \sum^{N_g - 1}_{i=0} \sum^{N_g - 1}_{j=0} p(i, j)^2 \
				\textnormal{ here, range = [0,1] }
			\end{equation}

		\item Contrast: It gives a measure of intensity contrast between a pixel
			and its neighbor over the whole image.

			\begin{equation}
				Con = \sum^{N_g -1}_{n=0} n^2 \sum^{N_g -1}_{i=0} \sum^{N_g
				-1}_{j=0} p(i,j)^2 \
				\textnormal{ here, range = [0,1] }
			\end{equation}

		\item Correlation: It gives a measure of how correlated a pixel to its
			neighbor over the whole image.

			\begin{equation}
				C = \frac{1}{\sigma^x \sigma^y}
				\sum^{N_g - 1}_{i=0} \sum^{N_g -1}_{j=0} (i,j) p(i,j)^2
				- \mu_x \mu_y \ \textnormal{here, range = [-1,1]}
			\end{equation}

		\item Homogeneity: It gives a measure of closeness of distribution of
			elements in GLCM to GLCM diagonal.

			\begin{equation}
				H = \sum^{N_g -1}_{i=0} \sum^{N_g -1}_{j=0}
				\frac{p(i,j)}{1 + \pmod{i,j}}
				\ \textnormal{here, range = [0, 1]}
			\end{equation}
	\end{enumerate}

	\subsection{Classification}%
	\label{sub:Classification}

	The Machine learning algorithms are used for
	classification of MR brain image either as normal or abnormal.  The major
	aim of ML algorithms is to automatically learn and make intelligent
	decisions. The feature set formed by above specified method was applied to
	Multi-Layer Perceptron (MLP) and Naive Bayes for classification.  MLP [3] is
	a feed forward artificial neural network model that maps sets of input data
	into a set of appropriate output. It is known as feed forward because it
	does not contain any cycles and network output depends only on the current
	input instance. In MLP, each node is a neuron with a nonlinear activation
	function. It is based on supervised learning technique. Learning take place
	by changing connection weights after each piece of data is processed, based
	on the amount of error in the target output as compared to the expected
	result. The goal of the learning procedure is to minimize error by improving
	the current values of the weight associated with each edge. Because of this
	backward changing process of the weights, model is named as
	back-propagation.

	Naive bayes is a supervised learning as well as statistical method for
	classification. It is simple probabilistic classifier based on Bayes
	theorem. It assumes that the value of a particular feature is unrelated to
	the presence or absence of any other feature. The prior probability and
	likelihood are calculated in order to calculate the posterior probability.
	The method of maximum posterior probability is used for parameter
	estimation. This method requires only a small amount of training data to
	estimate the parameters which are needed for classification. The time taken
	for training and classification is less.
